Model complexity and model choice for animal movement models

### 2016-06-14 guelph_talk/guelph_panther.Rnw
more on guelph talk
gitignore, guelph tweaks

\documentclass[english]{beamer}
\definecolor{links}{HTML}{2A1B81}
\hypersetup{colorlinks,linkcolor=,urlcolor=links}
\usepackage{natbib}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{color}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{animate}
\usepackage{arydshln}
\usepackage[normalem]{ulem}
\newcommand{\colemph}[1]{{\color{red} \emph{#1}}}
%\bibliographystyle{shortreflist}
\bibliographystyle{notitle}

@@

\begin{frame}
\frametitle{Acknowledgements}
\begin{description}
\item[People] \textbf{Michael Li}, \textbf{Madelon van de Kerk}, \\
Dave Onorato, Madan Oli
\item[Agencies] US Fish and Wildlife Service, US Geological Survey, US National Park Service
\item[Funding] NSERC Discovery grant, NSF IGERT program
\end{description}

@@

@@

% \tiny
\fontsize{3pt}{5pt}\selectfont
\bibliography{../paper}
\end{multicols}
\end{frame}

>>>>

\documentclass[english]{beamer}
\definecolor{links}{HTML}{2A1B81}
\hypersetup{colorlinks,linkcolor=,urlcolor=links}
\usepackage{natbib}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{color}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{animate}
\usepackage{arydshln}
\usepackage[normalem]{ulem}
\newcommand{\colemph}[1]{{\color{red} \emph{#1}}}
%\bibliographystyle{shortreflist}
\bibliographystyle{notitle}

@@

\begin{frame}
\frametitle{Acknowledgements}
\begin{description}
\item[People] \textbf{Michael Li}, \textbf{Madelon van de Kerk}, \\
Dave Onorato, Madan Oli; many unnamed field biologists
\item[Agencies] US Fish and Wildlife Service, US Geological Survey, US National Park Service
\item[Funding] NSERC Discovery grant, NSF IGERT program
\end{description}

@@

\begin{frame}
\includegraphics[width=\textwidth]{pix/panther2.jpg}

\url{http://tinyurl.com/panthermoves}; 
{\small
  \url{http://www.slideshare.net/bbolker/model-complexity-and-model-choice-for-animal-movement-models}}

@@

% \tiny
\fontsize{5pt}{7pt}\selectfont
\bibliography{../paper}
\end{multicols}
\end{frame}
